Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-10 Paper/ms.tex
nu oph figure
Courtney

\author[Brewer]{%
  Brendon~J.~Brewer$^{1}$\thanks{bj.brewer@auckland.ac.nz},
  % Courtney?
  \medskip\\
  $^1$Department of Statistics, The University of Auckland, Private Bag 92019, Auckland 1142, New Zealand}

@@

\vspace{-0.5cm}
\section*{Acknowledgements}
It is a pleasure to thank Courtney Donovan (Auckland) for many helpful
conversations about this subject. BJB is partially
supported by the Marsden Fund (Royal Society of New Zealand).

>>>>

\author[Brewer]{%
  Brendon~J.~Brewer$^{1}$\thanks{bj.brewer@auckland.ac.nz},
  Courtney P. Donovan$^{1}$
  \medskip\\
  $^1$Department of Statistics, The University of Auckland, Private Bag 92019, Auckland 1142, New Zealand}

@@

The posterior distribution for $N$, the number of planets, is shown in
Figure~\ref{fig:nu_oph_N}.

\begin{figure}
\includegraphics[scale=0.5]{Figures/nu_oph_N.eps}
\caption{The posterior distribution for the number of planets $N$ orbiting
$\nu$ Oph.\label{fig:nu_oph_N}}
\end{figure}

\vspace{-0.5cm}
\section*{Acknowledgements}
BJB is partially
supported by the Marsden Fund (Royal Society of New Zealand).
